Rawls For Electricity Planning Models

### 2025-06-03 Paper_Endogenous.tex

\begin{figure}
    \centering
    \subcaptionbox{2027}{\includegraphics[width=0.45\textwidth]{Figures/EndogenousResults/base_short/Dispatch_Relative_by_scenario_2027.png}}
    \subcaptionbox{2030}{\includegraphics[width=0.45\textwidth]{Figures/EndogenousResults/base_short/Dispatch_Relative_by_scenario_2030.png}}
    \caption{Generation by Technology by Scenario}
\end{figure}

\begin{figure}
    \centering
    \includegraphics[width=0.7\linewidth]{Figures/EndogenousResults/base_short/exposure_cost_PPF.png}
    \caption{Here we show the relationship between the objective function (min-max of exposure) and the cost limit constraint.}
    \label{PPF}
\end{figure}

>>>>

\begin{figure}
    \centering
    \subcaptionbox{2027}{\includegraphics[width=0.45\textwidth]{Figures/EndogenousResults/current_policies_short/Dispatch_Relative_by_scenario_2027.png}}
    \subcaptionbox{2030}{\includegraphics[width=0.45\textwidth]{Figures/EndogenousResults/current_policies_short/Dispatch_Relative_by_scenario_2030.png}}\\
    \subcaptionbox{2035}{\includegraphics[width=0.45\textwidth]{Figures/EndogenousResults/current_policies_short/Dispatch_Relative_by_scenario_2035.png}}
    \subcaptionbox{2040}{\includegraphics[width=0.45\textwidth]{Figures/EndogenousResults/current_policies_short/Dispatch_Relative_by_scenario_2040.png}}\\
    \subcaptionbox{2045}{\includegraphics[width=0.45\textwidth]{Figures/EndogenousResults/current_policies_short/Dispatch_Relative_by_scenario_2045.png}}
    \subcaptionbox{2050}{\includegraphics[width=0.45\textwidth]{Figures/EndogenousResults/current_policies_short/Dispatch_Relative_by_scenario_2050.png}}\\
    \caption{Generation by Technology by Scenario}
\end{figure}

\begin{figure}
    \centering
    \includegraphics[width=0.7\linewidth]{Figures/EndogenousResults/current_policies_short/exposure_cost_PPF.png}
    \caption{Here we show the relationship between the objective function (min-max of exposure) and the cost limit constraint.}
    \label{PPF}
\end{figure}
